\\textsc{Mathematical Description}

### 2022-06-28 100-math-description/GR-sslcm-math-description.Rmd
Include todolist package

---
title: "\\textsc{Mathematical Description}"
subtitle: "\\textsc{State-Space Life Cycle Model for Grande Ronde Spring Chinook Salmon}"
output: 
  bookdown::pdf_document2:
    keep_tex: false
    toc: true
    toc_depth: 3
    number_sections: true
    citation_package: natbib
  # bookdown::word_document2
fontfamily: mathpazo
geometry: margin=1in
linkcolor: cyan
urlcolor: cyan
citecolor: black
bibliography: cites.bib
link-citations: true
biblio-style: apalike
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{microtype}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \cfoot{\thepage}
  - \renewcommand{\headrulewidth}{0.5pt}
  - \renewcommand{\footrulewidth}{0.5pt}
  - \lfoot{State-Space Life Cycle Model\\Mathematical Description}
  - \rfoot{Grande Ronde Spring Chinook Salmon}
  - \usepackage{titlesec}
  - \titleformat{\section}{\bfseries\LARGE\scshape}{\thesection}{1em}{}
  - \titleformat{\subsection}{\bfseries\large}{\thesubsection}{1em}{}
  - \titleformat{\subsubsection}{\itshape}{\thesubsubsection}{1em}{}
  - \renewcommand{\contentsname}{Table of Contents}
  - \renewcommand{\eqref}[1]{\ref{#1}}
  - \renewcommand*{\log}{\mathrm{log}\hspace{-0.20em}}
  - \renewcommand*{\max}{\mathrm{max}\hspace{-0.20em}}
  - \newcommand{\logit}{\mathrm{logit}\hspace{-0.20em}}
  - \newcommand{\ilogit}{\mathrm{logit}^{-1}\hspace{-0.20em}}
  - \newcommand{\MVNdist}{\mathcal{MVN}\hspace{-0.20em}}
  - \newcommand{\Ndist}{\mathcal{N}\hspace{-0.20em}}
  - \newcommand{\Bdist}{\mathcal{B}\hspace{-0.20em}}
  - \newcommand{\Mdist}{\mathcal{M}\hspace{-0.20em}}
---

>>>>

---
title: "\\textsc{Mathematical Description}"
subtitle: "\\textsc{State-Space Life Cycle Model for Grande Ronde Spring Chinook Salmon}"
output: 
  bookdown::pdf_document2:
    keep_tex: false
    toc: true
    toc_depth: 3
    number_sections: true
    citation_package: natbib
  # bookdown::word_document2
fontfamily: mathpazo
geometry: [top=1in,bottom=1in,left=0.25in,right=1.75in]
linkcolor: cyan
urlcolor: cyan
citecolor: black
bibliography: cites.bib
link-citations: true
biblio-style: apalike
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{microtype}
  - \usepackage{float}
  - \usepackage{xcolor}
  - \definecolor{my-blue}{HTML}{E6F0FF}
  - \usepackage[textwidth=1.5in]{todonotes}
  - \setuptodonotes{backgroundcolor=my-blue,textcolor=black,linecolor=ProcessBlue,bordercolor=my-blue,size=footnotesize}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \cfoot{\thepage}
  - \renewcommand{\headrulewidth}{0.5pt}
  - \renewcommand{\footrulewidth}{0.5pt}
  - \lfoot{State-Space Life Cycle Model\\Mathematical Description}
  - \rfoot{Grande Ronde Spring Chinook Salmon}
  - \usepackage{titlesec}
  - \titleformat{\section}{\bfseries\LARGE\scshape}{\thesection}{1em}{}
  - \titleformat{\subsection}{\bfseries\large}{\thesubsection}{1em}{}
  - \titleformat{\subsubsection}{\itshape}{\thesubsubsection}{1em}{}
  - \renewcommand{\contentsname}{Table of Contents}
  - \renewcommand{\eqref}[1]{\ref{#1}}
  - \renewcommand*{\log}{\mathrm{log}\hspace{-0.20em}}
  - \renewcommand*{\max}{\mathrm{max}\hspace{-0.20em}}
  - \newcommand{\logit}{\mathrm{logit}\hspace{-0.20em}}
  - \newcommand{\ilogit}{\mathrm{logit}^{-1}\hspace{-0.20em}}
  - \newcommand{\MVNdist}{\mathcal{MVN}\hspace{-0.20em}}
  - \newcommand{\Ndist}{\mathcal{N}\hspace{-0.20em}}
  - \newcommand{\Bdist}{\mathcal{B}\hspace{-0.20em}}
  - \newcommand{\Mdist}{\mathcal{M}\hspace{-0.20em}}
---
